Influences of GDP in the U.S

### 2022-11-12 Manuscript/manuscript.tex
commit

In this equation, "(C) represents private-consumption expenditures by households and nonprofit organizations, investment (I) refers to business expenditures by businesses and home purchases by households, 
government spending (G) denotes expenditures on goods and services by the government, and net exports (NX) represents a nation’s exports minus its imports." (CITE BRITICANICA)
This equation is one that is learned in any introduction to macroeconomics courses. 
Calculating GDP is something that economists have accomplished and this equation is accepted in the industry. 
What economists are now researching is what factors impact Gross Domestic Product. 
There has been an abdunace of research in this field related to what variables are significant. 
Which factors have been researched are subjective based on those who are conducting the study.

@@

(cite GDP PARAdox) researches the critism behind GDP's influence in economies. They compare the understanding that even though GDP can influence economically relevant decisions, it does not factor in social welfare. 
Since GDP is a global indicator "The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries." (cite PARADOX)
They also touch on how government agencies and politicians strive to avoid low GDP. When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power (cite PARADOX)

@@

\begin{tabular}{ |p{2cm}||p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}| }
  \hline
  \multicolumn{7}{|c|}{Summary} \\
  \hline
  Variable & Min. & 1st Q & Median & Mean & 3rd Q & Max. \\
  \hline
  TPEC & 5.669 & 6.07& 7.609 & 7.462 & 8.082 & 9.965\\
  GDP &  1377 & 4341 & 8363 & 9962 & 14940 & 25248\\
  POP & 211192 & 238482 & 271709 & 273195 & 30886 & 332940\\
  TCMR & .6506 & 3.4607 & 6.1448 & 6.1156 & 8.054 & 14.8384\\
  DPI & 968.7 & 3114.2 & 6037.2 & 7440.5 & 11171.3 & 19586.5\\
  UNRATE & 3.6 & 5.05 & 5.867 & 6.231 & 7.3 & 12.967\\
  BSPL & 45.99 & 56.35 & 67.69 & 75.44 & 98.96 & 116.10\\
  \hline
\end{tabular}

>>>>

In this equation, "(C) represents private-consumption expenditures by households and nonprofit organizations, investment (I) refers to business expenditures by businesses and home purchases by households, 
government spending (G) denotes expenditures on goods and services by the government, and net exports (NX) represents a nation’s exports minus its imports" \citet[]{brit}.
This equation is one that is learned in any introduction to macroeconomics courses. 
Calculating GDP is something that economists have accomplished and this equation is accepted in the industry. 
What economists are now researching is what factors impact Gross Domestic Product. 
There has been an abdunace of research in this field related to what variables are significant. 
Which factors have been researched are subjective based on those who are conducting the study.

@@

\citet{van2009gdp} researches the critism behind GDP's influence in economies. They compare the understanding that even though GDP can influence economically relevant decisions, it does not factor in social welfare. 
Since GDP is a global indicator "The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries"\citet[]{van2009gdp}.
They also touch on how government agencies and politicians strive to avoid low GDP. When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power\citet[]{van2009gdp}.

@@

\begin{center}
\begin{tabular}{ |p{1.75cm}||p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}| }
  \hline
  \multicolumn{7}{|c|}{Summary} \\
  \hline
  Variable & Min. & 1st Q & Median & Mean & 3rd Q & Max. \\
  \hline
  TPEC & 5.669 & 6.07& 7.609 & 7.462 & 8.082 & 9.965\\
  GDP &  1377 & 4341 & 8363 & 9962 & 14940 & 25248\\
  POP & 211192 & 238482 & 271709 & 273195 & 30886 & 332940\\
  TCMR & .6506 & 3.4607 & 6.1448 & 6.1156 & 8.054 & 14.8384\\
  DPI & 968.7 & 3114.2 & 6037.2 & 7440.5 & 11171.3 & 19586.5\\
  UNRATE & 3.6 & 5.05 & 5.867 & 6.231 & 7.3 & 12.967\\
  BSPL & 45.99 & 56.35 & 67.69 & 75.44 & 98.96 & 116.10\\
  \hline
\end{tabular}
\end{center}
